Git Learning Notes

### 2014-02-03 ch-tms/tms.tex
tms reviews

Parallel with the scenario of graphene and CNT, TMDC few layer structures attracts intensive research efforts recently. The unfolded TMDC nanotubes exhibit many appealing features, i.e., indirect-to-direct band gap transition, valley electronics, and become a promising candidate in energy harvesting, optoelectronics.

For scientific research purpose, exfoliation by liquid or mechanics methods can provide plenty materials. Yet considering the integration into current microelectronic process, CVD synthesis of TMDC FL is desired, which hold the greatest potential for high yield production of \ce{MS2}. So in this work we focus on the CVD-based methods, as summarized in Table~\ref{tab:tmsgrowth}.

@@

% CVD TMDC
\begin{landscape}
\begin{table}[htb]
\centering
\caption{TMDC FL methods summary}\label{tab:tmsgrowth}
{\footnotesize
\begin{tabular}{lp{2in}p{4in}}
\toprule
TMDC  &  precursor & growth condition  \\
\midrule
\ce{WS2} & hot W filament (above 1500 \si{\degreeCelsius}) in Ar/\ce{O2} flow  & Cubic phase, PL, resistivity measured  \\
\addlinespace[0.5em]
& W filament DC heating in \ce{NH3} or \ce{N2}/\ce{H2} flow  & multi phases, 100mg per batch, stable dispersion in both organic and aqueous solvents  \\
\bottomrule
\end{tabular}
}
\end{table}
\end{landscape}

@@

@@

Lattice vibration in hexagonal \ce{MoS2} was studied by (Wieting & Verble, 1971) using infrared and Raman spectroscopy. 15 optical modes are allowed assuming 6 atoms in primitive cell. Refractive indices was calculated as n0= 3.9, ne = 2.5. \cite{Wieting1971}

Band structure  of \ce{MoS2} in bulk form was calculated by (Mattheiss, 1973). There is some controversy about the exact value of bandgap. The calculation result is 1.2eV ( indirect gap).\cite{Mattheiss1973}

Alkali metal intercalated \ce{WS2} film was prepared.(Homyonfer et al., 1997) Stage 6 superlattice formation was suggested according to X-ray diffraction, and photoresponse spectra and electron tunneling measurement were done.

(Ballif, Regula, & Lévy, 1999) annealing of W/S/W layer , a thin Ni layer deposition, Ni-W-S phase diagram.

Sulfurizaiton of W film, (Jäger-Waldau, Lux-Steiner, Jäger-Waldau, & Bucher, 1993)

(Splendiani et al., 2010) reported the PL in monolayer \ce{MoS2}.  Calculation indicated the indirect gap become larger when thinning, while the previous direct one almost stays as the same, the value is about 1.85eV (direct gap).\cite{Splendiani2010}

(Ramasubramaniam, Naveh, & Towe, 2011) investigate the band gap tuning in bilayer TMD materials by applying external E field. Similar research has been done for graphene and bilayer boron nitride. Semiconductor-metal transition was suggested for \ce{MoS2} and WS2, with difference on the CBM and VBM evolution. In \ce{MoS2}, the valence-band-splitting cause the A and B excitons in optical absorption measurement. Calculation shows that CB and VB are translated toward the Fermi level with increasing E field.  The external field localized charge along C axis, but delocalized that within the plane normal towards C, thereby driving the semi-metal transition. It was mentioned that this transition is not anticipated in monolayer \ce{MoS2}. It was emphasized that precise band gaps might be different from the author’s results, yet the gap-tuning should be universal.

(Kośmider & Fernández-Rossier, 2013) studied the heterojunction between two monolayers of \ce{MoS2} and WS2. Top of VB in W layer and bottom of CB in Mo layer, forming type II structure. bilayer gap 1.2 eV.

(Shi, Pan, Zhang, & Yakobson, 2013) studied the strained monolayer \ce{MoS2} and WS2. The results show that exciton binding energy is insensitive to the strain, while optical band gap becomes smaller as strain increases. Monolayer WS2 PL maximum located at about 1.95eV. Calculation shows the electron effective mass of WS2 is the smallest, rendering higher mobility in device.

(Zhou et al., 2010) heterojunction is employed to transferred photo-generated carriers. schottky barrier conduction band electron trapping and consequent longer electron-hole pair lifetimes. Numerous studies have suggested that fine particles of transition metals or their oxides, when dispersed on the surface of a photocatalyst matrix, can act as electron traps on n-type semiconductors.

(Ueno, Saiki, et al. 1990) Van der Waals epitaxial growth of transition metal dichalcogenides (TMD) on mica. ( MoSe2, NbSe2,
Method: MBE substrate temp : 500 \si{\degreeCelsius}

CVD of MoS2 by H2S and MoF6/MoCl5; MoS2 deposition temperature: 400-550 degree. (W. Y. Lee, Besmann, and Stott 1994)

thermal decomposition of (NH4)2MoO2S2 and intermediate product MoOS2 was studied. application: hyfrodesulfurization in refinery (Weber et al. 1996)

\cee{MoCl5 + 1/4S8 + 5/2H2 \rightarrow MoS2 + 5HCl} (Stoffels et al. 1999)

(Endler et al. 1999) solid-phase diagram for \ce{Mo-S-Cl-H-Ar} system at 1 kPa.

(M Remskar et al. 1999) WS2 nanotube from WO3-x whisker. heating 840 degree under flow of H2/N2/H2S ,

A detailed study by (Rothschild, Sloan, and Tenne 2000) tungsten filament oxidation by water. then WS2 nanotube from WO3-x whisker. heating 840 degree under flow of H2/N2/H2S ,

IF MoS2 synthesis by MoO3 nanobelt and S.(X. L. Li and Li 2003)

\begin{align}
\cee{WCl6 + S &rightarrow WS2 + Cl2S2}\\
\cee{MoCl5 + S &\rightarrow MoS2 + S2Cl2} \\
\cee{S2Cl2 + NaOH &\rightarrow NaCl + S + Na2SO3 + H2O}
\end{aligh}

WO3 and S by ball-milling (Z. Wu et al. 2010)

Inorganic core –shell nanotube, WS2@MoS2 core-shell NT.(Kreizman et al. 2010)

vdW Epitaxy of MoS2 on graphene. (Y. Shi et al. 2012)

(Zhan et al. 2012) 1-5nm thick Mo coating on SiO2/Si. Mo coating on Si did not work.

WS2 monolayer and intense photoluminescent behavior. Sulfurization of WO3 film( 5-20 angstrom). (Gutiérrez et al. 2012)

MoO3 on sapphire reduction in H2 at 500 and sulfurizatin at 1000 degree. (Lin et al. 2012)

quantitative Raman of MoS2 on insulating subs. intensity difference between supported and suspended was highlighted, detailed model in support info.(S.-L. Li et al. 2012)

MoS2 on SiO2/Si sub pretreated with OTAS, PTCDA solution. (Y.-H. Lee et al. 2012)

WO3-x (1nm) on SiO2/Si sulfurization at 750-950 degree, (Elías et al. 2013)

source MoS2 powder, Ar On sapphire, SiO2/Si, QWP circularly polarized  light (S. Wu et al. 2013)

MoO3 powder and Sulfur powder, pregrow purge, heating 600 degree, (Mann et al. 2013)

(Wang et al. 2013)
MoS2 CVD (tsinghua univ) layer by layer sulfurization of MoO2
MoO3 powder 25mg and MnO2 powder 25 mg, extra sulfur
Ar purging  20mins, heating at 650 degree to produce MoO2 flakes
Further reaction between MoO2 and S was performed at 850-950 degree under Ar flow.

MoS2 on SiO2, sapphire, and graphite by MoCl5 and S. (Yu et al. 2013)
growth time: 10min at 850 degree, P: 2 Torr.

MoO3 nanoribbon (Na2MoO4 hydrothermal method)sulphurization, (Najmaei et al. 2013)

review of inorganic 2D materials, (Chhowalla et al., 2013)

(Ramasubramaniam, 2012) decrease in dielectric screening and thereby enhanced excitonic effect.
DFT is not good at describing photoemission, GW approximation overcome this deficiency but still not enough for photoabsorption process in which ehps are created. BSE equation is used to compensate this discrepancy,
WX2 exhibits larger spin-orbit splitting as compared to MX2 family.

>>>>

Parallel with the scenario of graphene and CNT, TMDC few layer structures attracts intensive research efforts recently. The unfolded TMDC nanotubes exhibit many appealing features, i.e., indirect-to-direct band gap transition,\cite{Splendiani2010} valley electronics, and become a promising candidate in energy harvesting, optoelectronics.

For scientific research purpose, exfoliation by liquid \cite{Smith2011} or mechanical methods \cite{Lee2010a} can provide plenty materials. Yet considering the integration into current microelectronic process, CVD synthesis of TMDC FL is desired, which hold the greatest potential for high yield production of \ce{MS2}. So in this work we focus on the CVD-based methods, as summarized in Table~\ref{tab:tmsgrowth}.

\citeauthor{Lee1994} studied the CVD of \ce{MoS2} by \ce{MoCl5} or \ce{MoF6} and \ce{H2S} in great details. Phase diagrams for \ce{Mo-S-Cl-H} and \ce{Mo-S-F-H} system at 1 kPa were simulated. \citeauthor{Endler1999} also investigated the solid-phase diagram for \ce{Mo-S-Cl-H-Ar} system.\cite{Endler1999} It was found pure \ce{MoS2} was main product when molar ratio of \ce{H2S}-\ce{MoCl5} exceeds 2. More important, \ce{MoS2} basal plane orientation can be parallel to substrate when the thickness was smaller than 50 nm.

\citeauthor{Regula1997} studied the Ni-W-S phase diagram and the role of Ni layer in promoting \ce{WS2} film growth from amorphous \ce{WS3}.\cite{Regula1997} \emph{In-situ} TEM analysis confirmed the formation of \ce{NiS_x} droplets and lateral growth of \ce{WS2} from these droplets. \cite{Regula1998}

\citeauthor{Cong2013} prepared monolayer \ce{WS2} on 300nm \ce{SiO2}-Si by sulfurization of \ce{WO3} powders in a one-end sealed tube.\cite{Cong2013} It was suggested that pre-cleaning the inner tube by IPA and DI water could effectively increase the pressure of vapor source. This observation probably arise from the reduction of \ce{WO3} assisted by IPA and water residuals, or due to the possible presence of \ce{H2S}. Intermediate phase \ce{WO_yS_{2-y}} and \ce{WS_{2+x}} is proposed in the growth mechanism. Possible thick \ce{WS_{2+x}} flakes decompose subsequently, leading to ML \ce{WS2}. Sulfurization mechanism study of \ce{WO3} suggested \ce{W^{6+}} cannot be directly reduce to \ce{W^{4+}} in \ce{WS2}.\cite{VanderVlies2002,VanderVlies2002a} Tungsten oxysulfides was necessary as the intermediate phase. Other chalcogenide has also been synthesized using this one-end sealed layout.\cite{Mukherjee2013}

\citeauthor{Cao2014} studied the layer-dependence \ce{MoS2} electrocatalysis and propose the vertical hopping efficiency of electrons instead of the edge site numbers is a key factor for catalytic reaction.\cite{Cao2014} ref19,20

In studying the growth of TMDC, two issues dominate: one is the reaction of precursor, the other is the surface energy status of receiving substrates. For \ce{MoS2}, the reaction mechanism of \ce{MoO3} to \ce{MoS2} was studied by \citeauthor{Weber1996}.\cite{Weber1996} This study provided guideline for the recent syntheses of \ce{MoS2} by sulfurization of \ce{MoO3}. \cite{Lin2012,Lee2012b,Liu2012a}

@@

% CVD TMDC
\begin{landscape}
\begin{table}[htb]
\centering
\caption{TMDC FL methods summary}\label{tab:tmsgrowth}
{\footnotesize
\begin{tabular}{lp{2.5in}p{4.5in}}
\toprule
TMDC  &  precursor & growth condition (default temperature unit \si{\degreeCelsius}) \\
\midrule
\ce{MoS2} films \cite{Lee1994,Endler1999} & \ce{MoCl5}, \ce{H2S} & 1 kPa, temperature: 400-550 \si{\degreeCelsius}, 100/10/2.5 sccm for Ar, \ce{H2S} and \ce{MoCl5} flow\\
\addlinespace[0.5em]
\ce{MoS2} FL \cite{Zhan2012} & 1-5nm Mo films on \ce{SiO2}, Sulfur & purging, RT-550@30mins, 550-750@90mins and hold for 10 mins. Mo coating on Si did not work.\\
\ce{MoS2} FL \cite{Lin2012,Wang2013} & 4nm \ce{MoO3} coating on sapphire  & reduced to \ce{MoO2} in \ce{H2} and Ar at 500 \si{\degreeCelsius}, sulfurization at 850-1000 \si{\degreeCelsius} \\
\addlinespace[0.5em]
\ce{MoS2} FL \cite{Liu2012a} & \ce{(NH4)2MoS4} in DMF solution transport by Ar bubbler or dip-coating onto subs &  annealing under Ar or Ar + Sulfur, total pressure 0.2-2 Torr, \\
 \addlinespace[0.5em]
\ce{MoS2} FL \cite{Wu2013} & \ce{MoS2} powder & Ar flow, 900 \si{\degreeCelsius} heating, pressure 20 Torr, 650 \si{\degreeCelsius} growth\\
 \addlinespace[0.5em]
\ce{MoS2} FL \cite{Mann2013,Najmaei2013,Ji2013} Rice & \ce{MoO3} powders or ribbons, Sulfur & Ar flow, 530-850\si{\degreeCelsius}, total pressure 0.2-2 Torr, 5-30mins, mica or \ce{SiO2}-Si\\
 \addlinespace[0.5em]
\ce{MoS2} FL \cite{Lee2012b,Ling2014} & 18mg \ce{MoO3} powders, Sulfur,various seeding promoter on sub & 5sccm Ar, 650 \si{\degreeCelsius}, 3min growth, atmospheric pressure, quick cooling\\

 \midrule
\ce{WS2} films\cite{Ballif1999,Brunken2008} & sputtering \ce{WS_{3+x}} on 10nm Ni  & annealing under Ar for 1h at 850 \si{\degreeCelsius} \\
\addlinespace[0.5em]
\ce{WS2} FL \cite{Berkdemir2013} & $\sim$1nm \ce{WO3} coating on 285nm \ce{SiO2}-Si, 500mg sulfur & 800 \si{\degreeCelsius} for 30 mins, 100 sccm Ar, atmospheric pressure in \cite{Gutierrez2012} and 450 mTorr in \cite{Elias2013}. triangular flakes obtained\\
\addlinespace[0.5em]
\ce{WS2} ML \cite{Cong2013} & \ce{WO3} powder on sub1 covered by sub2, sulfur & 750 \si{\degreeCelsius} hold for 5mins, one-end sealed inner tube, 100 sccm Ar\\

\bottomrule
\end{tabular}
}
\end{table}
\end{landscape}

@@

\ce{WS2} NT chirality by TEM SEAD.\cite{Zhu2000}

hydrogen evolution catalysts. \cite{Merki2011}

\ce{WS2} NT FET. \cite{Levi2013}

\ce{WS2} NT transport \cite{Zhang2012c}

Raman substrate dependence \cite{Buscema2013}

@@

\begin{align}
\cee{WCl6 + S &\rightarrow WS2 + Cl2S2}\\
\cee{MoCl5 + S &\rightarrow MoS2 + S2Cl2} \\
\cee{S2Cl2 + NaOH &\rightarrow NaCl + S + Na2SO3 + H2O}
\end{align}

\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{ws2_ramsch}
\caption[CVD system]{Chemical vapor system and \cite{Ghorbani-asl}}
\label{fig:ws2ramsch}
\end{figure}

### 2014-02-03 figure_table.tex
tms reviews

% art work global settings
%  origin:
 all tick in, line color: blue or black, line width: 2; tick : 18pt;
 layout area(in): left:1, top:0.3; width 10: height 7; total
 layout area(in): left:1, top:0.8; width 9.6: height 7; total 12 by 9
 export: 3in auto
 text size: 22
% SEM
2.5in by 2in, 300dpi; gray scale

@@

A low recombination rate is preferred for high photocatalytic efficiency. The simultaneous migration of electrons and holes.
\textbf{\ce{WS2}-\ce{WO3}}: 1 kW light source(Hg, or Xe lamp), photon flux, phenol (\ce{C6H5OH}, 94.1g/mol, MP 40C)concentration is 20 mg/L, hydroxyl group. The quantitative analysis of phenol was performed via a standard colorimetric method.\footnote{\url{http://omlc.ogi.edu/spectra/PhotochemCAD/html/072.html}}
\citeauthor{DiPaola1999} prepared \ce{WS2}-\ce{WO3} mixture in two methods, sulfurization of \ce{WO3} and oxidation of \ce{WS2},with the latter are more active.
\citeauthor{DiPaola1999} also concluded that the actual efficiency of mixed \ce{WS2}-\ce{WO3} catalysts depends on the ratio of each composition present of the surface of the particles, and the maximum of photoactivity is obtained with 40-50\% surface molar ratio of \ce{WS2}.

@@

\citeauthor{Sreedhara2013} studied the kinetics of photodegradation of methylene blue\footnote{\ce{C16H18N3SCl},319.8 g/mol, MP: 100C accompanied with decomposition \url{http://en.wikipedia.org/wiki/Methylene_blue}} dye by few layer \ce{MoO3}.
For the photodegradation method, it was stated that `` the samples were collected after the photoreaction had been centrifuged for 5 min to remove the photocatalyst before UV-Vis measurement.''

\si{W/in^2}
\si{\degreeCelsius}

@@

>>>>

\subsection{artwork}
% art work global settings
%  origin:

 all tick in, line color: blue or black, line width: 2; tick : 18pt;
 layout area(in): left:1, top:0.3; width 10: height 7; total
 layout area(in): left:1, top:0.8; width 9.6: height 7; total 12 by 9
 export: 3in auto
 text size: 22
% SEM
2.5in by 2in, 300dpi; gray scale

@@

\subsection{photocatalyst}
A low recombination rate is preferred for high photocatalytic efficiency. The simultaneous migration of electrons and holes.
\textbf{\ce{WS2}-\ce{WO3}}: 1 kW light source(Hg, or Xe lamp), photon flux, phenol (\ce{C6H5OH}, 94.1g/mol, MP 40C)concentration is 20 mg/L, hydroxyl group. The quantitative analysis of phenol was performed via a standard colorimetric method.\footnote{\url{http://omlc.ogi.edu/spectra/PhotochemCAD/html/072.html}}
\citeauthor{DiPaola1999} prepared \ce{WS2}-\ce{WO3} mixture in two methods, sulfurization of \ce{WO3} and oxidation of \ce{WS2},with the latter are more active.
\citeauthor{DiPaola1999} also concluded that the actual efficiency of mixed \ce{WS2}-\ce{WO3} catalysts depends on the ratio of each composition present of the surface of the particles, and the maximum of photoactivity is obtained with 40-50\% surface molar ratio of \ce{WS2}.

@@

\citeauthor{Sreedhara2013} studied the kinetics of photodegradation of methylene blue\footnote{\ce{C16H18N3SCl},319.8 g/mol, MP: 100C accompanied with decomposition \url{http://en.wikipedia.org/wiki/Methylene_blue}} dye by few layer \ce{MoO3}.
For the photodegradation method, it was stated that `` the samples were collected after the photoreaction had been centrifuged for 5 min to remove the photocatalyst before UV-Vis measurement.''
\subsection{tms}
%%%%%%%%%%%% literature tms %%%%%%%%%

(Ramasubramaniam, Naveh, \& Towe, 2011) investigate the band gap tuning in bilayer TMD materials by applying external E field. Similar research has been done for graphene and bilayer boron nitride. Semiconductor-metal transition was suggested for \ce{MoS2} and WS2, with difference on the CBM and VBM evolution. In \ce{MoS2}, the valence-band-splitting cause the A and B excitons in optical absorption measurement. Calculation shows that CB and VB are translated toward the Fermi level with increasing E field.  The external field localized charge along C axis, but delocalized that within the plane normal towards C, thereby driving the semi-metal transition. It was mentioned that this transition is not anticipated in monolayer \ce{MoS2}. It was emphasized that precise band gaps might be different from the author’s results, yet the gap-tuning should be universal.

(Shi, Pan, Zhang, \& Yakobson, 2013) studied the strained monolayer \ce{MoS2} and WS2. The results show that exciton binding energy is insensitive to the strain, while optical band gap becomes smaller as strain increases. Monolayer WS2 PL maximum located at about 1.95eV. Calculation shows the electron effective mass of WS2 is the smallest, rendering higher mobility in device.

(Kośmider \& Fernández-Rossier, 2013) studied the heterojunction between two monolayers of \ce{MoS2} and WS2. Top of VB in W layer and bottom of CB in Mo layer, forming type II structure. bilayer gap 1.2 eV.

Lattice vibration in hexagonal \ce{MoS2} was studied by (Wieting & Verble, 1971) using infrared and Raman spectroscopy. 15 optical modes are allowed assuming 6 atoms in primitive cell. Refractive indices was calculated as n0= 3.9, ne = 2.5. \cite{Wieting1971}

Band structure  of \ce{MoS2} in bulk form was calculated by (Mattheiss, 1973). There is some controversy about the exact value of bandgap. The calculation result is 1.2eV ( indirect gap).\cite{Mattheiss1973}

Alkali metal intercalated \ce{WS2} film was prepared.(Homyonfer et al., 1997) Stage 6 superlattice formation was suggested according to X-ray diffraction, and photoresponse spectra and electron tunneling measurement were done.

Sulfurizaiton of W film, (Jäger-Waldau, Lux-Steiner, Jäger-Waldau, & Bucher, 1993)

(Splendiani et al., 2010) reported the PL in monolayer \ce{MoS2}.  Calculation indicated the indirect gap become larger when thinning, while the previous direct one almost stays as the same, the value is about 1.85eV (direct gap).\cite{Splendiani2010}

(Zhou et al., 2010) heterojunction is employed to transferred photo-generated carriers. schottky barrier conduction band electron trapping and consequent longer electron-hole pair lifetimes. Numerous studies have suggested that fine particles of transition metals or their oxides, when dispersed on the surface of a photocatalyst matrix, can act as electron traps on n-type semiconductors.

thermal decomposition of (NH4)2MoO2S2 and intermediate product MoOS2 was studied. application: hyfrodesulfurization in refinery (Weber et al. 1996) \cite{Weber1996}

\cee{MoCl5 + 1/4S8 + 5/2H2 \rightarrow MoS2 + 5HCl} (Stoffels et al. 1999)

(M Remskar et al. 1999) WS2 nanotube from WO3-x whisker. heating 840 degree under flow of H2/N2/H2S ,

A detailed study by (Rothschild, Sloan, and Tenne 2000) tungsten filament oxidation by water. then WS2 nanotube from WO3-x whisker. heating 840 degree under flow of H2/N2/H2S ,

IF MoS2 synthesis by MoO3 nanobelt and S.(X. L. Li and Li 2003)

Inorganic core –shell nanotube, WS2@MoS2 core-shell NT.(Kreizman et al. 2010)

vdW Epitaxy of MoS2 on graphene. (Y. Shi et al. 2012)

WS2 monolayer and intense photoluminescent behavior. Sulfurization of WO3 film( 5-20 angstrom). (Gutiérrez et al. 2012)

MoO3 on sapphire reduction in H2 at 500 and sulfurizatin at 1000 degree. (Lin et al. 2012)

quantitative Raman of MoS2 on insulating subs. intensity difference between supported and suspended was highlighted, detailed model in support info.(S.-L. Li et al. 2012)

MoS2 on SiO2/Si sub pretreated with OTAS, PTCDA solution. (Y.-H. Lee et al. 2012)

WO3-x (1nm) on SiO2/Si sulfurization at 750-950 degree, (Elías et al. 2013)\cite{Elias2013}

source MoS2 powder, Ar On sapphire, SiO2/Si, QWP circularly polarized  light (S. Wu et al. 2013)

(Wang et al. 2013)
MoS2 CVD (tsinghua univ) layer by layer sulfurization of MoO2
MoO3 powder 25mg and MnO2 powder 25 mg, extra sulfur
Ar purging  20mins, heating at 650 degree to produce MoO2 flakes
Further reaction between MoO2 and S was performed at 850-950 degree under Ar flow.

MoS2 on SiO2, sapphire, and graphite by MoCl5 and S. (Yu et al. 2013)
growth time: 10min at 850 degree, P: 2 Torr.

review of inorganic 2D materials, (Chhowalla et al., 2013)

(Ramasubramaniam, 2012) decrease in dielectric screening and thereby enhanced excitonic effect.
DFT is not good at describing photoemission, GW approximation overcome this deficiency but still not enough for photoabsorption process in which ehps are created. BSE equation is used to compensate this discrepancy,
WX2 exhibits larger spin-orbit splitting as compared to MX2 family.

reaction mechanism of \ce{MoO3} to \ce{Mo2S}.\cite{Weber1996}

\citeauthor{Ling2014} studied the role of seeding promoters in CVD growth of FL \ce{MoS2}.\cite{Ling2014} PTAS treated substrates provided nucleation site and thus enable uniform deposition of \ce{MS2}.  This enhancement perhaps arise from the \ce{K+} ions.

%%%%%%%%%%%%%%%%%%%%%%
\subsection{figure table units}
\si{W/in^2}
\si{\degreeCelsius}

@@

\subsection{chromic}
